Specifying and Verifying the Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
Make our weakness (no push-button verif.) less verbose and more clear

It should be noted that our verification tool does not target the
class of bugs that can be detected automatically (\emph{push-button
  verification}). Instead, stencil computation bugs must be
identified relative to a specification of the intended behaviour.

>>>>

Our verification tool does not target the
class of bugs that can be detected automatically (\emph{push-button
  verification}). Instead, stencil computation bugs must be
identified relative to a specification of the intended access pattern.
